The \emph{FrobeniusThresholds} package for \emph{Macaulay2}

### 2019-06-06 Fsing/FThresholdsPaper/FThresholds.tex
Minor changes to intro

\subsection*{Some background and notation}  
The functionality implemented in the \emph{FrobeniusThresholds} is not restricted to nonsingular ambient rings (see Section \ref{sec.IsFPT}).
However, for most of this article, we work in a polynomial ring over a finite field of  characteristic $p>0$, and we remain in this case throughout the introduction for the sake of clarity.  
Unless otherwise stated, all polynomials and ideals under consideration are regarded as elements in such a ring.  The ideal of this ring generated by the ring's variables is denoted $\idealm$.

Let us roughly outline the way in which many natural numerical invariants in prime characteristic commutative algebra are constructed:  For every natural number $e$, associate to some fixed set of data|often, a collection of polynomials and ideals|an integer describing something of relevance that depends on $e$ (e.g., the dimension of some interesting vector space constructed in terms of your initial data).   Finally, normalize this integer by dividing by some power of $p^e$, and take the limit as $e$ approaches infinity.

>>>>

\subsection*{Some background and notation}  
It is important to note that much of the functionality implemented in the \emph{FrobeniusThresholds} is not restricted to regular ambient rings; see Section \ref{sec.IsFPT} for a prominent example of this.

However, for the sake of concreteness, we will mostly work in a polynomial ring over a finite field of  characteristic $p>0$.  In fact,  we will work in this context exclusively in this introduction.  Thus, unless otherwise stated, all polynomials and ideals under consideration are regarded as elements in such a ring.  The ideal of this ring generated by its variables is denoted $\idealm$.

Let us outline a common way in which natural numerical invariants in prime characteristic commutative algebra are constructed:  For every natural number $e$, associate to some fixed set of data|often, a collection of polynomials and ideals|an integer describing something of relevance that depends on $e$ (e.g., the dimension of some interesting vector space constructed in terms of your initial data).   Finally, normalize this integer by dividing by some power of $p^e$, and then take the limit as the integer $e$ tends to infinity.  The resulting limit, should it exist, should then encode some interesting information about your initial set of data.
